### 2020-01-01 docs/thesis-project/article.tex
Update article.tex

\section{Membership Management Frameworks}\label{sec:membership-management}

Gossip-based protocols, also know has epidemic protocols, gained popularity in the nineties for their usability to solve problems like database replication, failure detection, and resource-monitoring. In this section, we present two such protocols used for membership management, i.e., used to keep current partial views of large-scale, dynamic networks, built on unstructured overlays. Just like we mentioned in section \ref{sec:p2p-overlays}, keeping a view of all peers in the system is not a solution. Another fundamental issue of unstructured networks is to avoid partitioning. The following alternatives are both scalable, robust, and decentralized solutions to both these problems. Likewise, peers act autonomously in order to provide self-organization or self-healing capabilities to the overlays in which the protocols are applied.

\subsection{Cyclon} Cyclon\cite{cyclon} is useable even in highly dynamic environments, providing peer degree symmetry, low diameter, low clustering, resilience to churn, and massive node failures. The focus of the authors was to provide a lightweight and simple protocol. It consists of having each peer keeping an ever-changing, partial view, with fixed-size \textit{c}, of the network in a structure called \textit{neighbors}. Periodically, independently and asynchronously, a peer contacts a random neighbor to exchange acquaintances. This process is called \textit{shuffling}. During a shuffle, a peer \textit{i}, first increments the age of all his known neighbors by one. Then, selects the oldest of all his neighbors, \textit{j}, and $l-1$ other random neighbors, forming \textit{s}. Then \textit{i} replaces \textit{j}'s network address by his own and sets his age to zero, in \textit{s}. After that, \textit{i} sends \textit{s} to \textit{j} and waits for \textit{j} to reply with \textit{s'}. Unlike \textit{s}, \textit{s'} is composed of a purely random subset of \textit{j}'s neighbors, without any age modifications. Upon reception of subsets \textit{s} and \textit{s'}, \textit{j} and \textit{i}, respectively, update their \textit{neighbors} by first using any empty slots in their partial views and then by replacing entries which they sent to the other, i.e., if \textit{i} has no more slots, he replaces, in its \textit{neighbors} structure, the entries that he sent in \textit{s} to \textit{j}, with the ones he received in \textit{s'} from \textit{j}. Note that, after \textit{i} initiates a shuffle with \textit{j}, \textit{i} becomes \textit{j}'s neighbor, but \textit{j} is no longer a neighbor to \textit{i}, i.e., the neighboring relation between \textit{i} and \textit{j} is reversed. Unlike many protocols, Cyclon links between peers are not bidirectional.

The age is essential in the shuffling algorithm, for two reasons. First, it limits the lifetime of each peer in \textit{neighbors} structures, which globally bounds the number of existing pointers to them, it also limits the time each peers' addresses are passed around until they are selected as shuffling targets, resulting on a more up-to-date overlay as well as uniform distribution of each peers' addresses over the network.

When a peer leaves the overlay for any reason, the remaining peers may have to remove him from their \textit{neighbors} structure. Timely removal is fundamental for the robustness of the overlay.  Cyclon uses passive detection. Whenever a peer \textit{i} contacts \textit{j} for shuffling and obtains no response it assumes \textit{j} is disconnected and removes it from his \textit{neighbors}. Since the time for \textit{i} to contact \textit{j} is bounded by the age property in \textit{neighbors}, detection is accelerated.

Cyclon simulations show that the average path length and clustering coefficient, for various configurations, converged to values similar to those found in random graphs, i.e., converged to small-diameter topologies with low clustering. Gossip-based protocols often have high clustering, which is undesirable both in terms of robustness and overhead. Another exciting result of Cyclon is that the average path length increased logarithmically, and clustering decreased exponentially, as the number of peers in the network increased, hence demonstrating scalability and increased robustness.

The authors also propose a join method that does not disrupt the randomness of the obtained overlays, while simultaneously making new peers indistinguishable from old ones. Whenever \textit{i} wishes to join the overlay, he contacts one peer \textit{j} already in the overlay who initiates \textit{c} random-walks with time-to-live (TTL) equal to the average path length of the overlay. The peer \textit{k} where the random-walk ends, replaces one of his \textit{neighbors} entries with \textit{i} network address, setting \textit{i} age set to zero and sends the replaced entry to \textit{i}. Note that even if some of the random walks do not complete due to byzantine failures, \textit{i} will remain connected to the overlay and will eventually find new acquaintances.

We conclude by reinforcing that Cyclon provides good self-healing and self-organization capabilities without complex algorithms or apparent downsides other than the one where too few peers in the system may cause it to be under performant due to clustering effects. In a way, it relates to BlatAnt since the proposal passively bounds the diameter of the network.

\subsection{Newscast}
In Newscast \cite{newscast-computing}, all peers proactively exchange, timestamped, information with each other, including not only neighboring information but also app-specific information, allowing for simplified implementation of aggregation algorithms, i.e., finding statistics regarding for example network size. Newscast is responsible for membership-management and a second function, which does not exist in Cyclon, which is information dissemination.

In Newscast, there is a separation of responsibilities. Within each peer, there are two types of entities. Those who run the newscast protocol, are called \textit{corespondents}. Those who run processes of a distributed application are called \textit{agents}. \textit{Correspondents} run the same instance of the newscast protocol. \textit{Agents} are not required to run the same application. Each \textit{agent} has one or more \textit{correspondents}. This separation does not explicitly exist in Cyclon. Each \textit{agent} implements an interface with two functions \textit{getNews()} and \textit{newsUpdate(news[])}. The \textit{correspondent} uses the former to request news from their \textit{agent}, and the latter to deliver app-specific news collected from other peers' \textit{correspondents} in the network. Each \textit{correspondent} as a fixed-size news cache of size \textit{c} and periodically exchange news with each other has followed: request news to the \textit{agent}, timestamp them along with the local time, and IP-address of the \textit{agent}, then storing them in a cache entry. Afterward, it selects another peer's IP address running the same \textit{correspondent} aggregation function, as available in his cache. Both \textit{correspondents} exchange the entirety of their caches and pass the merged cache with $2c+1$ entries to their respective \textit{agents} before discarding the oldest entries, after timestamp normalization, down to \textit{c} and storing the results themselves. The timestamp normalization is not a clock-synchronization process and has some inaccuracy, but as long as transmission times between two peers are not too big, there should be no problem. During the discarding process, the algorithm ensures that there is at most one news item per \textit{agent}.

It is debatable if Newscast has an advantage over Cyclon since news exchange messages already include peer addresses, leading to a transparent resolution of the membership problem. Cyclon, however, has several advantages over Newscast. These include: the resulting overlays of Cyclon have better randomness due to its shuffling-based algorithm, whereas Newscast and other gossip-based management frameworks, seem to have small-world properties according to previous research \cite{eval-gossip-based}. Like in Cyclon, disconnected peers are eventually forgotten due to the timestamp property of the newscasting process. Newly joined peers' cache initialization is based on a regular news exchange with one or more peers who are already members of the overlay. In contrast, Cyclon uses \textit{c} random-walks exchanging exactly one cache entry with possibly different peers, which in turn helps to maintain the randomness properties; finally, while Newscast managed to achieve their goals of providing a robust, scalable, adaptive and lightweight solution for simultaneous membership management and aggregation Cyclon exhibits less network overhead\cite{cyclon}.

@@

Many academic and commercial projects have been developed over the years where cloud, grid, and other centralized architectures are partly assisted by P2P networks. In these systems, peers are usually machines belonging to the clients of the service, and they help to decrease the load on the system, hence reducing its cost. This approach is especially prevalent in streaming and online gaming services, for example, Blizzard Activision uses their player base to help distribute installers and patches in a P2P fashion, and Digital Extremes uses, in their free-to-play game Warframe, P2P networks in particular, but not all, group missions where individuals are in instances of the game inaccessible by players outside the group. However, only recently, was the alternative explored, where P2P networks serve the vast majority of the service and are assisted by stable cloud services only to help guarantee some quality of service property of the system under critical situations. We present two of them.

\subsection{Cloudcast}
Cloudcast \cite{cloudcast} is a P2P-assisted cloud architecture that differs from other proposals because it does not offload the provided service to peers only when service availability is not affected. Furthermore, the architecture does not augment P2P systems with elastic computing nodes that perform particular tasks beyond the reach of the P2P network, such has bulk-synchronous content distribution. Cloudcast functionality depends solely on a passive storage service that transparently integrates into a gossip-based P2P system. The reasoning behind not using elastic computing instances is to eliminate fixed renting costs. Like that, the focus is on minimizing the costs associated with storage and bandwidth. The architecture uses two gossip protocols, one for membership management and another for information dissemination. Key results of the proposal include: accesses to the cloud service are bounded regardless of the number of clients in the system; the cloud service only distributes content when few peers are available; the overlay does not suffer from partitioning regardless of the number of peers in the system; the two illustrated use cases have an absurdly low yearly cost when compared to pure cloud approaches, and finally the authors recognize that the vast part of their bill is tied to membership management and not to actual storage costs, thus using strategies that adapt to the size of the network could yield even better savings.

The passive cloud storage service is a key-value store that can be accessed via GET and PUT operations, but it cannot under any circumstance initiate communications with the system peers. Two problems are identified, \textit{membership management} and \textit{information diffusion}. To solve the first problem, Cloudcast uses the Cyclon protocol to do peer-sampling. From other alternatives, Cyclon was chosen not for its particular inexpensiveness, but because the protocol maintains a random overlay topology that works even during high churn periods and even in the presence of catastrophic failures where up to 80\% of the peers fail. Cyclon properties also guarantee that references to the cloud server are not too many keeping usage cost under control. Finally, the cloud server can easily integrate in the protocol, in particular, Cyclon does not require the cloud server to initiate any communications, i.e., its active roles can be carried out by peers interacting with it; Finally, the cloud server can easily integrate into the protocol, in particular, Cyclon does not require the cloud server to initiate any communications, i.e., its active roles can be carried out by peers interacting with it; In this regard, the dummy process carried by the peers occasionally refreshes pointers to the cloud to avoid losing all references to it in the system. To deal with the case where all references cloud are lost due to the dynamic characteristics of the environment, e.g. churn and lost messages, all peers keep a logical timestamp of the last round they heard about the cloud server updating it whenever they successfully contact it or because one of their a \textit{neighbor} heard about it more recently then them, if after \textit{t} rounds peer has not updated this timestamp he will create a new cloud reference with probability $p\textsubscript{recovery}$.

The second problem is solved using two different implementations of gossip algorithms explained in depth in \cite{epidemic_algorithms}. They are a \textit{rumor-mongering, coin and blind} approach which favors fast news spreading and consists in having a peer \textit{i} periodically forwarding updates he learns about to some other peer \textit{j}, then deciding with probability $p\textsubscript{rumor}$ if he should, permanently, stop gossiping the update; And a \textit{anti-entropy, push-pull} approach which guarantees that news are eventually known by all participants of the system and consists in having each peer \textit{i} periodically contacting a random neighbor \textit{j} to exchange update they know about. All updates to the data are recorded in the cloud server through a PUT operation before becoming hot-topics, thus triggering rumor-mongering. Peers never contact the cloud server for rumor-mongering purposes. The anti-entropy approach can be piggybacked to the Cyclon peer-sampling step, thus decreasing message overhead; the authors, however, do not mention this optimization.

@@

\begin{algorithm}[ht]
\caption{MakeDecision(N\textsubscript{e}), replicaOverlay}
\label{alg:makedecision}
\begin{algorithmic}
    \If {$N\textsubscript{e}\geq S$}
        \State $replicaOverlay.Neighbors.Remove(CloudReference)$\
        \If {$N\textsubscript{e} > R$}
            \State $p\textsubscript{yes} \gets \dfrac{N\textsubscript{e} - R}{N\textsubscript{e}}$
            \State $this.LeaveOverlay(replicaOverlay, p\textsubscript{yes})$
        \State $replicaOverlay.Protocol \gets cyclon$
        \EndIf
    \ElsIf {$C < N\textsubscript{e} < S$}
        \State $N\textsubscript{a} \gets [\dfrac{S(1 + k)}{N\textsubscript{e}} - 1]$
        \State $newNeighbors \gets GetNewNeighbors(this.UnderlyingOverlay, N\textsubscript{a})$
        \State $newNeighbors.Send(this.RandomView(replicaOverlay))$
        \State $replicaOverlay.Neighbors.Add(newNeighbors)$
        \State $replicaOverlay.Protocol \gets cloudcast$
    \ElsIf{$Ne \leq C$}
        \State $N\textsubscript{a} \gets [\dfrac{S(1 + k)}{N\textsubscript{e}} - 1]$
        \State $newNeighbors \gets GetNewNeighbors(this.UnderlyingOverlay, N\textsubscript{a})$
        \State $newNeighbors.Send(this.RandomView(replicaOverlay) \cup CloudReference)$
        \State $replicaOverlay.Neighbors.Add(newNeighbors \cup CloudReference)$
        \State $replicaOverlay.Protocol \gets cloudcast$
    \EndIf
\end{algorithmic}
\end{algorithm}

Following the suggestions of Cloudcast authors, H. Kavalionak \textit{et al.}, developed a decentralized algorithm \cite{marriage_of_convinience} that aims to do replica management in cloud-based, peer-assisted applications. Because the proposed work has no running title, we shall refer to it as ARM. The goal of the ARM is to maintain an appropriate replication level, despite churn, such that, at all times, at least one replica is available and ensuring that replicas survive failures. Furthermore, the proposal acknowledges that replicas should be synchronized, i.e., the system provides at least some consistency guarantees. In simple terms, this is perhaps the main difference between the proposed work and Cloudcast, which stores all updates in an always-on passive cloud server, helping with information diffusion and overlay connectivity and overall reliability of the system in extreme conditions. Cloudcast monetary cost reductions are primarily associated with limiting access to the cloud server. ARM effectively reduces those costs even further by performing timely switches between Cloudcast and regular Cyclon protocols, depending on the size of the network. To estimate the network size without centralization or broadcasting algorithms that would ultimately lead to either bottlenecks or overhead, ARM leverages a gossip-based aggregation method \cite{gossip-based_aggregation} that allows each peer to infer the approximate size of the network autonomously, at the end of each epoch. Estimation accuracy is dependent only on the size of the epoch. Likewise, the execution cost depends on the length of the epochs and the network churn rate, but not on the number of peers in the system, which means that ARM keeps the scale-free properties of the unstructured overlays that used in Cloudcast. The peers randomly organize themselves according to the Cyclon peer-sampling protocol, but depending on the results of the aggregation, the passive cloud-server used in Cloudcast is removed or kept in the overlay. In ARM, each data object to be replicated as its \textit{replica-overlay} on top of the regular unstructured overlay, which facilitates synchronization and cloud-usage decisions. The ARM algorithm is designed to consider four replica-overlay states, separated by three size thresholds: \textit{Critical (C)}, \textit{Sufficient (S)} and \textit{Redundant (S)}. \textit{C} depends on the chosen redundancy method, i.e., file-level \textit{vs.} block-level replication and is the sum of the minimum number of replicas required for data recovery plus the number of peers that will leave during the cloud backup replication phase. \textit{S} depends on the churn-rate and is the sum of \textit{C} plus the number of peers expected between two successive recovery phases. Finally, \textit{R} is a system parameter dependent also on the chosen redundancy method and is application requirements specific.  The aggregation method mentioned earlier is the foundation \textit{monitoring phase}, which consists of a fixed number of gossip and idle rounds, allowing a peer to infer the \textit{expected size (N\textsubscript{e})} of the replica-overlay and decide if he should add or remove the cloud or peers to the replica-overlay as well as the protocol he uses, based on Algorithm \ref{alg:makedecision}. After each monitoring phase, each peer calculates how long it should wait before executing the \textit{monitoring phase} again. That time depends mostly on \textit{N\textsubscript{e}}, e.g., if the state is below the critical threshold, the monitoring phase will initiate earlier than if it is above the redundant threshold, allowing the system to respond to overlay changes promptly and to keep the overlay size in a range that minimizes overhead but ensures that data does not become unavailable. The authors do not specify how much savings the system was capable of achieving using ARM; however, we can assume it is a substantial value; In Fig. \ref{fig:arm_results}, the plot on top displays the number of peers in the underlying network as a function of time, and the bottom plot shows the in-degree to the cloud server as a function of time, comparing Cloudcast and ARM (labeled as "our protocol").

@@

\newpage\section{Probabilistic Swarm Guidance}\label{sec:psg}
Markov chains describe a sequence of possible events in which the probability of each event depends only on the previous event states, often used to model real-world processes, such as queues of customers arriving at an airport and population growths. Markov processes are the basis for stochastic simulation methods known as Markov Chain Monte Carlo (MCMC), which allow one to perform random sampling over vast state spaces, i.e., computing expectations concerning complex, high dimensional probability distributions. The idea behind MCMC is creating a Markov Chain, which will, over time, tend to an equilibrium that is close to desired density distribution. In robotics and control areas Markov Chains and MCMC are used as the basis foundation for a process known as probabilistic swarm guidance, which gifts autonomous robots with the capability of generating their trajectories independently of each other, in decentralized fashion and without ahead-of-time position allocation, so that sets of robots, known as swarm, converges to the desired distribution shape. Swarm guidance has the advantage over other methods for this problem because robots do not necessarily need to communicate with each other to perform their tasks, even if they could gain from it; their overall distribution can be adapted dynamically to the environment, and any damage to their desired formation is eventually self-repaired. Demonstration of these properties can be found in recent research by B. Açikmeçe \textit{et al.} \cite{psg-mca, psg-caa}, which inspired us to apply swarm guidance principles to P2P networks and file survivability. Boyd et al. \cite{fast_mixing_mc} argue that the most popular MCMC methods, Metropolis-Hastings and Maximum-Degree Chain, that allow the creation of transition matrices, that can then be followed independently by autonomous robots in order to practice swarm guidance behavior are not optimal with respect to mixing rates, i.e.,  these algorithms may not result in matrices that converge in small amount of steps towards the desired density distribution. They propose that the problem of obtaining such matrices can be formulated as a convex optimization problem and prove that, for most cases, the resulting matrices have higher mixing rates. It is reasonable to assume that, concerning our problem in P2P networks, this might open the possibility of imposing additional constraints on the creation of the transition matrix, e.g., bounding the probability of a peer sending a file to some other peer in his hive to increase bandwidth balancing.

>>>>

\section{Membership Management Frameworks}\label{sec:membership-management}
Gossip-based protocols are well known for their usability to solve problems like database replication, failure detection, and resource-monitoring. We present two frameworks used for membership management that ensure peers keep up to date partial views of large-scale, dynamic networks, built on unstructured overlays using such protocols. Just like we mentioned in section \ref{sec:p2p-overlays}, keeping a view of all peers in the system is often not a solution. Another fundamental issue in P2P is how to avoid partitioning. The following alternatives are both scalable, robust, and decentralized solutions to both these problems. They gift peers with autonomous capabilities regarding self-organization and overlay healing.

\subsection{Cyclon} Cyclon\cite{cyclon} is useable even in highly dynamic environments, providing peer degree symmetry, low diameter, low clustering, resilience to churn, and massive node failures. The focus of the authors was to provide a lightweight and simple protocol. It consists of having each peer keeping an ever-changing, partial view, with fixed-size \textit{c}, of the network in a structure called \textit{neighbors}. Periodically, independently and asynchronously, a peer contacts a random neighbor to exchange acquaintances. This process is called \textit{shuffling}. During a shuffle, a peer \textit{i}, first increments the age of all his known neighbors by one. Then, selects the oldest of all his neighbors, \textit{j}, and $l-1$ other random neighbors, forming \textit{s}. Then \textit{i} replaces \textit{j}'s network address by his own and sets his age to zero, in \textit{s}. After that, \textit{i} sends \textit{s} to \textit{j} and waits for \textit{j} to reply with \textit{s'}. Unlike \textit{s}, \textit{s'} is composed of a purely random subset of \textit{j}'s neighbors, without any age modifications. Upon reception of subsets \textit{s} and \textit{s'}, \textit{j} and \textit{i}, respectively, update their \textit{neighbors} by first using any empty slots in their partial views and then by replacing entries which they sent to the other, i.e., if \textit{i} has no more slots, he replaces, in its \textit{neighbors} structure, the entries that he sent in \textit{s} to \textit{j}, with the ones he received in \textit{s'} from \textit{j}. Note that, after \textit{i} initiates a shuffle with \textit{j}, \textit{i} becomes \textit{j}'s neighbor, but \textit{j} is no longer a neighbor to \textit{i}, effectively reversing neighboring relation between both peers\footnote{Cyclon links are not bidirectional, conversely to the majority of protocols.}. The age is essential in the shuffling algorithm, for two reasons. First, it limits the lifetime of each peer in neighboring structures, which globally bounds the number of existing pointers to them. Secondly, it also limits the time each peers' addresses are passed around until they are selected as shuffling targets, resulting in a more up-to-date overlay as well as uniform distribution of each peers' addresses over the network. When a peer leaves the overlay for any reason, the remaining peers may have to remove him from their \textit{neighbors} structure. Many authors argue that timely removal is fundamental for the robustness of the overlay, Cyclon uses a reactive pessimistic policy that works as follows: Whenever a peer \textit{i} contacts \textit{j} for shuffling and obtains no response it assumes \textit{j} is disconnected and removes it from his \textit{neighbors}. Since the time for \textit{i} to contact \textit{j} is bounded by the age property, detection is accelerated, which is a property Gia does not have.

Cyclon simulations show that the average path length and clustering coefficient, for various configurations, converged to values similar to those found in random graphs, i.e., converged to small-diameter topologies with low clustering. Gossip-based protocols often have high clustering, which is undesirable both in terms of robustness and overhead. Another exciting result of Cyclon is that the average path length increased logarithmically, and clustering decreased exponentially, as the number of peers in the network increased, hence demonstrating scalability and increased robustness. Noting this property, the authors propose a join method that does not disrupt the randomness of the obtained overlays. Whenever \textit{i} wishes to join the overlay, he contacts one peer \textit{j} already in the overlay who initiates \textit{c} random-walks with time-to-live (TTL) equal to the average path length of the overlay. The peer \textit{k} where the random-walk ends, replaces one of his \textit{neighbors} entries with \textit{i} network address, setting \textit{i} age set to zero and sends the replaced entry to \textit{i}. Note that even if some of the random walks do not complete due to byzantine failures, \textit{i} will remain connected to the overlay and will eventually find new acquaintances. Cyclon as no apparent downsides other than the one where too few peers in the system may cause it to be under performant due to clustering effects, but this is expected in other solutions too. We note that in a certain way, this framework relates to BlatAnt since it implicitly bounds the diameter of the network.

\subsection{Newscast}
In Newscast \cite{newscast-computing}, all peers proactively exchange, timestamped, information with each other, including not only neighboring information but also app-specific information, allowing for simplified implementation of aggregation algorithms, i.e., finding statistics regarding for example network size. Newscast is thus responsible for both membership management as well as information dissemination. Within each Newscast peer, there are two types of entities. Those who run the actual newscast protocol, are called \textit{corespondents}. Those who run the distributed application are called \textit{agents}. \textit{Correspondents} all run the same instance of the newscast protocol. \textit{Agents} are not required to run the same distributed application. Each \textit{agent} has one or more \textit{correspondents}; this responsibility separation does not explicitly exist in Cyclon. Each \textit{agent} implements an interface with two functions \textit{getNews()} and \textit{newsUpdate(news[])}. The \textit{correspondent} uses the former to request news from their \textit{agent}, and the latter to deliver app-specific news collected from other peers' \textit{correspondents} in the network. Each \textit{correspondent} as a fixed-size news cache of size \textit{c} and periodically exchange news with each other has followed: request news to its \textit{agent}, timestamp them along with the local time, and IP-address of the peer, then store the news in a cache entry. Afterward, it selects another peer's IP address running the same type of \textit{correspondent}, as available in his cache. Both \textit{correspondents} exchange the entirety of their caches and pass the merged cache with $2c+1$ entries to their respective \textit{agents} before discarding the oldest entries, after timestamp normalization, down to \textit{c} and storing the results themselves. The timestamp normalization is not a clock-synchronization process and has some inaccuracy, but as long as transmission times between two peers are not too big, there should be no problem. During the discarding process, the algorithm ensures that there is at most one news item per \textit{agent} in the cache.

Newscast as a slight edge over Cyclon, due to graciously accounting for aggregation functions in its native protocol. Similarly, inactive peers are eventually forgotten due to the timestamp property, but we believe that Cyclon has several significant advantages. These include: the resulting overlays of Cyclon have better randomness due to its shuffling-based algorithm, whereas Newscast and other gossip-based management frameworks, seem to have small-world properties according to previous research \cite{eval-gossip-based}. Also, Cyclon uses logical timestamps; hence, no clock synchronization is required, not even a relaxed one. Newly joined peers' cache initialization is based on a regular news exchange with one or more peers who are already members of the overlay. In contrast, Cyclon uses \textit{c} random-walks exchanging exactly one cache entry with possibly different peers, which in turn helps to maintain overlay randomness; finally, while Newscast managed to achieve their goals of providing a robust, scalable, adaptive and lightweight solution, Cyclon exhibits less network overhead and can easily be extended to perform aggregation.

@@

Many academic and commercial projects have been suggested and used over the years where cloud and other centralized architectures are partly assisted by P2P networks; In these systems, peers are usually clients of the service, who help to decrease the load on the central system, hence reducing its cost. Examples include Spotify and Wuala until approximately five years ago. However, these approaches are still prevalent in streaming and online gaming services. Blizzard Activision uses their player base to help distribute installers and patches in a P2P fashion, and Digital Extremes uses, in their free-to-play game Warframe, P2P networks in particular, but not all, group missions where individuals are in instances of the game inaccessible by players outside the group. However, only recently, was the alternative experimented, where P2P networks serve the vast majority of the service and are assisted by stable cloud services only to help guarantee some quality of service property of the system under critical situations.

\subsection{Cloudcast}
Cloudcast \cite{cloudcast} is a P2P-assisted cloud architecture that differs from previous approaches because it does not offload the provided service to peers only when service availability is not at risk of being affected. Furthermore, the architecture does not augment P2P systems with elastic computing nodes that perform particular tasks beyond the reach of the P2P network, e.g., bulk-synchronous content distribution. Cloudcast functionality depends only on a passive storage service that transparently integrates into a gossip-based P2P system. The reasoning behind not using elastic computing instances is to eliminate fixed renting costs. Like that, the focus is on minimizing the costs associated with storage and bandwidth. The architecture uses two gossip protocols, one for membership management and another for information dissemination. Key results of the proposal include: i) accesses to the cloud service are bounded regardless of the number of clients in the system; ii) the cloud server only distributes content when few peers are available; iii) the overlay does not suffer from partitioning regardless of the number of peers in the system; iv) the two illustrated use cases have an absurdly low yearly cost when compared to pure cloud approaches; iv) authors imply that most of the expected bill is tied to membership management and not to actual storage costs, suggesting that strategies that adapt to the size of the network could yield better savings.

The passive cloud storage service is a key-value store that can be accessed via GET and PUT operations, but it cannot under any circumstance initiate communications with the system peers. Two problems are identified, \textit{membership management} and \textit{information diffusion}. To solve the first problem, Cloudcast uses the Cyclon protocol to do peer-sampling. From other alternatives, Cyclon was chosen not for its particular inexpensiveness, but because the protocol maintains a random overlay topology that works even during high churn periods and even in the presence of catastrophic failures where up to 80\% of the peers fail. Cyclon properties also guarantee that cloud server has a bounded in-degree, keeping usage cost under control. Finally, the cloud server can easily integrate into Cyclon because the latter does not require the cloud server to initiate any communications, i.e., its active roles can be carried out by peers interacting with it; In this regard, the dummy process carried by the peers occasionally refreshes pointers to the cloud to avoid losing all references to it in the system. To deal with the case where all cloud references are lost due to the dynamicity of the environment and unreliability of the network layer, all peers keep a logical timestamp of the last round they heard about the cloud server updating it whenever they successfully contact it or because one of their a \textit{neighbor} heard about it more recently then them. If after \textit{t} rounds a peer has not updated this timestamp he will create a new cloud reference with probability $p\textsubscript{recovery}$. The second problem is tackled by implementing two gossip algorithms. They are a \textit{rumor-mongering, coin and blind} approach which favors fast news spreading and consists in having a peer \textit{i} periodically forwarding updates he learns about to some other peer \textit{j}, then deciding with probability $p\textsubscript{rumor}$ if he should stop rumoring; And a \textit{anti-entropy, push-pull} approach which guarantees that news are eventually known by all peers by having each peer \textit{i} periodically contacting a random neighbor \textit{j} to exchange updates they know about. All updates to the data are recorded in the cloud server through PUT operations before being rumored. Peers never contact the cloud server for rumor-mongering purposes. We suggest that anti-entropy messages can be piggybacked to the peer-sampling messages, decreasing the number of messages passed in the network; the authors, however, do not implement this optimization.

@@

\begin{algorithm}[t]
\caption{MakeDecision(N\textsubscript{e}), replicaOverlay}
\label{alg:makedecision}
\begin{algorithmic}
    \If {$N\textsubscript{e}\geq S$}
        \State $replicaOverlay.Neighbors.Remove(CloudReference)$\
        \If {$N\textsubscript{e} > R$}
            \State $p\textsubscript{yes} \gets \dfrac{N\textsubscript{e} - R}{N\textsubscript{e}}$
            \State $this.LeaveOverlay(replicaOverlay, p\textsubscript{yes})$
        \State $replicaOverlay.Protocol \gets cyclon$
        \EndIf
    \ElsIf {$C < N\textsubscript{e} < S$}
        \State $N\textsubscript{a} \gets [\dfrac{S(1 + k)}{N\textsubscript{e}} - 1]$
        \State $newNeighbors \gets GetNewNeighbors(this.UnderlyingOverlay, N\textsubscript{a})$
        \State $newNeighbors.Send(this.RandomView(replicaOverlay))$
        \State $replicaOverlay.Neighbors.Add(newNeighbors)$
        \State $replicaOverlay.Protocol \gets cloudcast$
    \ElsIf{$Ne \leq C$}
        \State $N\textsubscript{a} \gets [\dfrac{S(1 + k)}{N\textsubscript{e}} - 1]$
        \State $newNeighbors \gets GetNewNeighbors(this.UnderlyingOverlay, N\textsubscript{a})$
        \State $newNeighbors.Send(this.RandomView(replicaOverlay) \cup CloudReference)$
        \State $replicaOverlay.Neighbors.Add(newNeighbors \cup CloudReference)$
        \State $replicaOverlay.Protocol \gets cloudcast$
    \EndIf
\end{algorithmic}
\end{algorithm}

Following the suggestions of Cloudcast authors, H. Kavalionak \textit{et al.}, developed a decentralized algorithm\cite{marriage_of_convinience} that aims to do replica management in cloud-based, peer-assisted applications. Because the proposed work has no running title, we shall refer to it as ARM. The goal of the ARM is to maintain an appropriate replication level, despite churn, such that, at all times, at least one replica is available and ensuring that replicas survive failures. Furthermore, the proposal acknowledges that replicas should be synchronized, i.e., the system should support session guarantees. The main difference between ARM and Cloudcast is that in the latter, the cloud server stores all updates in an always-on passive cloud server helping with information dissemination when needed, whereas, in the former, the cloud does not participate in the system at all, unless conditions are extreme. Cloudcast monetary cost reductions are thus, primarily associated with limiting access to the cloud server, and ARM effectively reduces those costs further by performing timely switches between Cloudcast and regular Cyclon protocols, depending on the size of the network. To estimate the network size without centralization or broadcasting that would ultimately lead to either bottlenecks or overhead, ARM leverages a gossip aggregation method that allows each peer to infer the approximate size of the network autonomously, at the end of each epoch. Estimation accuracy is dependent only on the size of the epoch. Likewise, the execution cost depends on the length of the epochs and the network churn rate, but not on the number of peers in the system, which means that ARM keeps the scale-free properties of the unstructured overlays that used in Cloudcast. The peers randomly organize themselves according to the Cyclon peer-sampling protocol, but depending on the results of the aggregation, the passive cloud-server used in Cloudcast is removed or kept in the overlay. In ARM, each data object to be replicated as its \textit{replica-overlay} on top of the regular unstructured overlay, which facilitates synchronization and cloud-usage decisions. The ARM algorithm is designed to consider four replica-overlay states, separated by three size thresholds: \textit{Critical (C)}, \textit{Sufficient (S)} and \textit{Redundant (S)}. \textit{C} depends on the chosen redundancy method, i.e., file-level \textit{vs.} block-level replication and is the sum of the minimum number of replicas required for data recovery plus the number of peers that will leave during the cloud backup replication phase. \textit{S} depends on the churn-rate and is the sum of \textit{C} plus the number of peers expected between two successive recovery phases. Finally, \textit{R} is a system parameter dependent also on the chosen redundancy method and is application requirements specific.  The aggregation method mentioned earlier is the foundation \textit{monitoring phase}, which consists of a fixed number of gossip and idle rounds, allowing a peer to infer the \textit{expected size (N\textsubscript{e})} of the replica-overlay and decide if he should add or remove the cloud or peers to the replica-overlay as well as the protocol he uses, based on Algorithm \ref{alg:makedecision}. After each monitoring phase, each peer calculates how long it should wait before executing the \textit{monitoring phase} again. That time depends mostly on \textit{N\textsubscript{e}}, e.g., if the state is below the critical threshold, the monitoring phase will initiate earlier than if it is above the redundant threshold, allowing the system to respond to overlay changes promptly and to keep the overlay size in a range that minimizes overhead but ensures that data does not become unavailable. The authors do not specify how much savings the system was capable of achieving using ARM; however, we can assume it is a substantial value; In Fig. \ref{fig:arm_results}, the plot on top displays the number of peers in the underlying network as a function of time, and the bottom plot shows the in-degree to the cloud server as a function of time, comparing Cloudcast and ARM (labeled as "our protocol").

@@

\section{Probabilistic Swarm Guidance}\label{sec:psg}
Markov chains describe a sequence of possible events in which the probability of each event depends only on the previous event states, often used to model real-world processes, such as queues of customers arriving at an airport and population growths. Markov processes are the basis for stochastic simulation methods known as Markov Chain Monte Carlo (MCMC), which allow one to perform random sampling over vast state spaces, i.e., computing expectations concerning complex, high dimensional probability distributions. The idea behind MCMC is creating a Markov Chain, which will, over time, tend to an equilibrium that is close to desired density distribution. In robotics and control areas Markov Chains and MCMC are used as the basis foundation for a process known as probabilistic swarm guidance, which gifts autonomous robots with the capability of generating their trajectories independently of each other, in decentralized fashion and without ahead-of-time position allocation, so that sets of robots, known as swarm, converges to the desired distribution shape. Swarm guidance has the advantage over other methods for this problem because robots do not necessarily need to communicate with each other to perform their tasks, even if they could gain from it; their overall distribution can be adapted dynamically to the environment, and any damage to their desired formation is eventually self-repaired. Demonstration of these properties can be found in recent research by B. Açikmeçe \textit{et al.} \cite{psg-mca, psg-caa}, which inspired us to apply swarm guidance principles to P2P networks and file survivability. Boyd et al. \cite{fast_mixing_mc} argue that the most popular MCMC methods, Metropolis-Hastings and Maximum-Degree Chain, that allow the creation of transition matrices, that can then be followed independently by autonomous robots in order to practice swarm guidance behavior are not optimal with respect to mixing rates, i.e.,  these algorithms may not result in matrices that converge in small amount of steps towards the desired density distribution. They propose that the problem of obtaining such matrices can be formulated as a convex optimization problem and prove that, for most cases, the resulting matrices have higher mixing rates. It is reasonable to assume that, concerning our problem in P2P networks, this might open the possibility of imposing additional constraints on the creation of the transition matrix, e.g., bounding the probability of a peer sending a file to some other peer in his hive to increase bandwidth balancing.
